Scoring Patients

### 2017-01-04 Patient Report.Rmd
Looking at different clustering methods

## Gamma = 250
```{r cors, echo=F, message=T, warning=F, fig.height=6, fig.width=6, fig.align='left'}
## Thresholds
min.probes=67 # equiv to 1MB
gamma2 = 250
sd.threshold = 0.08
gain.threshold = 1.1
loss.threshold = 0.9

>>>>

## Gamma = 250
```{r cors, echo=F, message=T, warning=F, fig.height=6, fig.width=6, fig.align='left'}
## Cluster the samples by coverage then pull out regions

## Thresholds
min.probes=67 # equiv to 1MB
gamma2 = 250
sd.threshold = 0.08  # cov by numbers of probes

gain.threshold = 1.1
loss.threshold = 0.9
